hormones

### 2019-12-12 analysis/07_hormones.Rmd
new GO analysis

```{r correlations}
PETCP <- left_join(prolactin2, PETC, by = "bird_id") %>% drop_na()
PETCP$treatment.x <- factor(PETCP$treatment.x, levels = alllevels2)
PETCP$hormone.y

@@

```{r manipulation}
# prolactin, removal only
hormones %>% 
    filter( hormone == c("prolactin"))  %>% 
    filter(treatment %in% c("inc.d3", "m.inc.d3", "inc.d9", "m.inc.d9", "inc.d17", "m.inc.d17", "hatch","m.n2"))  %>% 
  ggplot(aes(x = treatment, y = plasma_conc, fill = treatment,  color = sex)) +
    geom_boxplot() + 
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          legend.position = "none",
          strip.text = element_blank()) +
    scale_fill_manual(values = colorscharmaip) +
    scale_color_manual(values = sexcolors) +
    labs(y = "PRL (ng/mL)", x = NULL) +
    ylim(c(-16,100)) +

   annotation_custom(inc, xmax = 1.6, ymin = -14, ymax = 5) +
   annotation_custom(bldg, xmax = 3.6, ymin = -14, ymax = 5) +
   annotation_custom(inc, xmax = 5.6, ymin = -14, ymax = 5) +
   annotation_custom(bldg, xmax = 7.6, ymin = -14, ymax = 5) +
  annotation_custom(hatch, xmax = 9.6, ymin = -14, ymax = 5) +
  annotation_custom(bldg, xmax = 11.6, ymin = -14, ymax = 5) +
  annotation_custom(nestling, xmax = 13.6, ymin = -14, ymax = 5) +
  annotation_custom(bldg, xmax = 15.6, ymin = -14, ymax = 5) +

@@

hormones %>% 
    filter( hormone == c("prolactin"))  %>% 
    filter( treatment %in% c("inc.d9", "m.inc.d8", "inc.d17", "prolong", "hatch", "extend", "n5"))  %>% 
  ggplot(aes(x = treatment, y = plasma_conc, fill = treatment,  color = sex)) +
    geom_boxplot() + 
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          legend.position = "none",
          strip.text = element_blank()) +
    scale_fill_manual(values = colorscharmaip) +
    scale_color_manual(values = sexcolors) +
    labs(y = "PRL (ng/mL)", x = NULL) +
  ylim(c(-12,100)) +
   annotation_custom(inc, xmax = 1.6, ymin = -10, ymax = 10) +
   annotation_custom(hatch, xmax = 3.6, ymin = -10, ymax = 10) +
   annotation_custom(inc, xmax = 5.6, ymin = -10, ymax = 10) +
   annotation_custom(inc, xmax = 7.6, ymin = -10, ymax = 10) +
  annotation_custom(hatch, xmax = 9.6, ymin = -10, ymax = 10) +
  annotation_custom(hatch, xmax = 11.6, ymin = -10, ymax = 10) +
  annotation_custom(nestling, xmax = 13.6, ymin = -10, ymax = 10) +

>>>>

```{r correlations}
PETCP <- left_join(prolactin2, PETC, by = "bird_id") %>% drop_na()
PETCP$treatment.x <- factor(PETCP$treatment.x, levels = alllevels2)

@@

```{r manipulation}
# prolactin, removal only
hormones %>% 
    filter( hormone == c("prolactin"))  %>% 
    filter(treatment %in% c("inc.d3", "m.inc.d3", "inc.d9", "m.inc.d9", "inc.d17", "m.inc.d17", "hatch","m.n2"))  %>% 
  ggplot(aes(x = treatment, y = plasma_conc, fill = treatment,  color = sex)) +
    geom_boxplot() + 
  theme_B3()  +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          legend.position = "none",
          strip.text = element_blank()) +
    scale_fill_manual(values = colorscharmaip) +
    scale_color_manual(values = sexcolors) +
    labs(y = "PRL (ng/mL)", x = NULL) +
    ylim(c(-16,100)) +

   annotation_custom(inc, xmax = 1.6, ymin = -14, ymax = 5) +
   annotation_custom(removeegg, xmax = 3.6, ymin = -14, ymax = 5) +
   annotation_custom(inc, xmax = 5.6, ymin = -14, ymax = 5) +
   annotation_custom(removeegg, xmax = 7.6, ymin = -14, ymax = 5) +
  annotation_custom(hatch, xmax = 9.6, ymin = -14, ymax = 5) +
  annotation_custom(removeegg, xmax = 11.6, ymin = -14, ymax = 5) +
  annotation_custom(nestling, xmax = 13.6, ymin = -14, ymax = 5) +
  annotation_custom(removechick, xmax = 15.6, ymin = -14, ymax = 5) +

@@

hormones %>% 
    filter( hormone == c("prolactin"))  %>% 
    filter( treatment %in% c("inc.d9", "m.inc.d8", "inc.d17", "prolong", "hatch", "extend", "n5"))  %>% 
  ggplot(aes(x = treatment, y = plasma_conc, fill = treatment,  color = sex)) +
    geom_boxplot() + 
  theme_B3()  +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          legend.position = "none",
          strip.text = element_blank()) +
    scale_fill_manual(values = colorscharmaip) +
    scale_color_manual(values = sexcolors) +
    labs(y = "PRL (ng/mL)", x = NULL) +
  ylim(c(-12,100)) +
   annotation_custom(inc, xmax = 1.6, ymin = -10, ymax = 10) +
   annotation_custom(maniphatch, xmax = 3.6, ymin = -10, ymax = 10) +
   annotation_custom(inc, xmax = 5.6, ymin = -10, ymax = 10) +
   annotation_custom(manipinc, xmax = 7.6, ymin = -10, ymax = 10) +
  annotation_custom(hatch, xmax = 9.6, ymin = -10, ymax = 10) +
  annotation_custom(maniphatch, xmax = 11.6, ymin = -10, ymax = 10) +
  annotation_custom(nestling, xmax = 13.6, ymin = -10, ymax = 10) +
